---
title: "Introduction to lamyflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to lamyflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(lamyflow)
```

## The purpose of lamyflow

This is a introduction the Rpackage "lamyflow". This package helps to reproduce the github page [lamy-m.github.io](https://lamy-m.github.io/index.html) and some extra's.It contains 4 data files and 4 functions. 

## Installation 

The package "lamyflow" needs to be installed as following:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("lamy-m/lamyflow")
```

After installation the package can be called as following: 

```{r}
library(lamyflow)
```

## The datasets

This package contains four datasets that have been used in the github page [lamy-m.github.io](https://lamy-m.github.io/index.html). To load in the wanted datases use the function `{data}`

### Dataset: Celegans

The "Celegans" data set is been used in the [C. elegans plate experiment analysis](https://lamy-m.github.io/c.-elegans-plate-experiment-analysis.html). It contains 34 colomns and 360 rows. The data set can be load in as following:

```{r}
data("Celegans")
```

### Dataset: dengue

The "dengue" dataset is been used in the [Relational databases](https://lamy-m.github.io/relational-databases.html). It contains 6 colomns and 6,590 rows. The data set can be load in as following:

```{r}
data("dengue")
```

### Dataset: edcc_data

The "edcc_data" dataset is been used in the [Parameters and Presentations](https://lamy-m.github.io/parameters-and-presentations.html). It contains 11 colomns and 28,729 rows. The data set can be load in as following:

```{r}
data("edcc_data")
```

### Dataset: flu

The "flu" dataset is been used in the [Relational databases](https://lamy-m.github.io/relational-databases.html). It contains 6 colomns and 19,111 rows. The data set can be load in as following:

```{r}
data("edcc_data")
```

## The functions

This packages contains four functions. The functions can be used after the packaged is installed and loaded. The names of the functions in this package are: 

- Celegans_norm 
- datainfo
- csv_rds
- q_value

Use "?" before the function to see their documentation and what they do. 

```{r, eval=FALSE}
?Celegans_norm 
?datainfo
?csv_rds
?q_value
```
